Reference Tracking Strategies of Deaf Adult Signers in Turkish Sign Language

### 2023-01-31 revised_manuscript.Rmd
update

df_table_2 <- read.csv("./appendix/tables/table_tier.csv", sep = ";")
apa_table(df_table_2,
          caption ="Annotation Tiers with their Tags and Descriptions",
          note = "NOM = nominal, PRO = pronominal, CL = classifier, NULL = null anaphora.",
          escape = FALSE,
          align = c("p{3.2cm}", rep("p{3.8cm}", ncol(df_table_2))),
          placement = "p",
          font_size = "footnotesize",
          landscape = FALSE
)
```

>>>>

df_table_2 <- read.csv("./appendix/tables/table_tier.csv", sep = ";")
apa_table(df_table_2,
          caption ="Annotation Tiers with their Tags and Descriptions",
          note = "NOM = nominal, PRO = pronominal, CL = classifier, ZERO = zero anaphora.",
          escape = FALSE,
          align = c("p{3.2cm}", rep("p{3.8cm}", ncol(df_table_2))),
          placement = "p",
          font_size = "footnotesize",
          landscape = FALSE
)
```

### 2023-01-31 revised_manuscript.tex
update

\begin{tabular}{p{3.2cm}p{3.8cm}p{3.8cm}}
\toprule
Tier & \multicolumn{1}{c}{Tag} & \multicolumn{1}{c}{Description}\\
\midrule
Clause Boundary &  & The boundary between clauses indicated by the presence of predicates and/or certain prosodic cues (e.g., head nod)\\
Discourse Status & Introduced & A first mention of an entity in a given discourse regardless of any syntactic role\\
 & Maintained & A subject referent continued across two or more immediate clauses\\
 & Reintroduced & A subject referent discontinued across at least one clause\\
RE Type & NOM: Bare Noun & A non-modified noun phrase (e.g., CAT, MOUSE)\\
 & NOM: Modified Noun & A noun phrase modified by an index sign or an adjective\\
 & NOM: Fingerspelled Noun & Borrowed nouns from Turkish spelled by the manual alphabet (e.g., K-E-D-İ ‘cat’)\\
 & PRO: Pronominal IX & An index sign used in isolation to refer to an entity in discourse\\
 & CL: Whole Entity Classifier & A handshape that refers to the entirety of an entity\\
 & CL: Body Part Classifier & A handshape that refers to a part of an entity\\
 & CL: Handling Classifier & A handshape that refers to the handling of an item\\
 & CL: Extension Classifier & A handshape that denotes the size and shape of an entity\\
 & NULL: Constructed Action & A multifunctional construction where the signers take on the role of a referent and perform their actions\\
 & NULL: Plain Verb & A non-agreeing predicate (e.g., LOVE)\\
 & NULL: Agreement Verb & A predicate the beginning and ending of which agree with the person and number\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{tablenotes}[para]
\normalsize{\textit{Note.} NOM = nominal, PRO = pronominal, CL = classifier, NULL = null anaphora.}
\end{tablenotes}

>>>>

\begin{tabular}{p{3.2cm}p{3.8cm}p{3.8cm}}
\toprule
Tier & \multicolumn{1}{c}{Tag} & \multicolumn{1}{c}{Description}\\
\midrule
Clause Boundary &  & The boundary between clauses indicated by the presence of predicates and/or certain prosodic cues (e.g., head nod)\\
Discourse Status & Introduced & A first mention of an entity in a given discourse regardless of any syntactic role\\
 & Maintained & A subject referent continued across two or more immediate clauses\\
 & Reintroduced & A subject referent discontinued across at least one clause\\
RE Type & NOM: Bare Noun & A non-modified noun phrase (e.g., CAT, MOUSE)\\
 & NOM: Modified Noun & A noun phrase modified by an index sign, classifier etc.\\
 & NOM: Fingerspelled Noun & Borrowed nouns from Turkish spelled by the manual alphabet (e.g., K-E-D-İ ‘cat’)\\
 & PRO: Pronominal IX & An index sign used in isolation to refer to an entity in discourse\\
 & CL: Whole Entity Classifier & A handshape that refers to the entirety of an entity\\
 & CL: Body Part Classifier & A handshape that refers to a part of an entity\\
 & CL: Handling Classifier & A handshape that refers to the handling of an item\\
 & CL: Extension Classifier & A handshape that denotes the size and shape of an entity\\
 & ZERO: Constructed Action & A multifunctional construction where the signers take on the role of a referent and perform their actions\\
 & ZERO: Plain Verb & A non-agreeing predicate (e.g., LOVE)\\
 & ZERO: Agreement Verb & A predicate the beginning and ending of which agree with the person and number\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{tablenotes}[para]
\normalsize{\textit{Note.} NOM = nominal, PRO = pronominal, CL = classifier, ZERO = zero anaphora.}
\end{tablenotes}
